A new method to estimate dark matter halo concentrations

### 2015-01-14 paper/article.tex
added info about the steps for te MH

We sample the likelihood function distribution defined by ${\cal
  L}(c)=\exp(-\chi^2(c)/2)$ with a Metropolos-Hastings algorithms to
find the optimum value of $c$ and its  associated uncertainty
$\sigma_c$.

{\bf Cuantos pasos usa la cadena? (50000) De cuanto es el sigma en
los saltos de c en lca cadena? (0.029)

Falta alguna figura que muestre resultados de la -log likelihood para
algunos casos representativos.
}

>>>>

We sample the likelihood function distribution defined by ${\cal
  L}(c)=\exp(-\chi^2(c)/2)$ with a Metropolis-Hastings algorithm to
find the optimum value of $c$ and its  associated uncertainty
$\sigma_c$. We used 50000 steps for walk, where each step was randomly generated
with a normal distribution centered around the last step with an standard
deviation of $\sigma=0.03$.
